An efficient acyclic contact planner for multiped robots

### 2017-01-11 body/overview.tex
[Overview - Andrea_s comment]

Figure~\ref{fig:framework} illustrates our workflow.
\Pa and \Pb are addressed sequentially: we first plan a root guide path \deladp{with the \textit{reachability condition}}, before
extending it into a sequence of configurations in static equilibrium.

@@

\subsection{Computation of a guide path --- \Pa}
We first consider the problem of planning a root guide path (Figure~\ref{fig:framework}--$\mathcal{P}_1$).  The dimension of the path is equal to the number of degrees of freedom of the root of the robot.
\repadp{Similarly to}{As for} previous work~\citep{Bouyarmane2009} the path must be \textit{equilibrium feasible}: the root configurations \deladp{of the path} must be \repadp{extensible}{extended} into full-body static equilibrium configurations. Previous work verifies \textit{equilibrium feasibility} by explicitly computing such a \deladp{joint} configuration. 
We preserve the low dimensionality of the problem by approximating \textit{equilibrium feasibility} with \textit{contact rechability}, illustrated in the following.

An intuitive description of \gls{contact reachable} configurations is ``close, but not too close'' \addadp{to the environment}: close, because a contact surface must be partially included in the reachable workspace of the robot (represented for the right leg in Figure~\ref{fig:contact_gen}--a) to allow contact creation; not too close, because the robot must avoid collision.
\deladp{\textit{Contact reachability} is verified with the \textit{reachability condition}, a geometrical criterion based on this intuitive description (Figure~\ref{fig:reach_cond}).}
More precisely, a root configuration is \textit{contact reachable} if the root scaled by a \addadp{user-defined} factor $s \geq 1$ is not in collision, while the reachable workspace is in collision.
%~ Verifying the \textit{reachability condition} is very efficient in practice.
To plan a root path, we then use an RRT planner where, instead of checking collision to validate a configuration, we verify the \textit{reachability condition}.
This is detailed in Section~\ref{rbprm}.
%~ In Section~\ref{rbprm} we detail how  we define and use the \textit{reachability condition} to compute a guide path with the Reachability-Based RRT (Figure~\ref{fig:framework}---\Pa).

@@

The algorithm takes advantage of the fact that each root configuration is fixed to generate the contact by considering each limb individually. Candidate limb configurations resulting in the end-effector being close to the environment are selected from a database (\repadp{computed offline independently}{independent} from the environment).
Then we select one of these configurations based on user-defined heuristics (Figure~\ref{fig:contact_gen}), detailed in Appendix~\ref{sec:heuristics}.

@@

\section{Notation \deladp{conventions} and definitions} \label{notations}

>>>>

Figure~\ref{fig:framework} illustrates our workflow.
\Pa and \Pb are addressed sequentially: we first plan a root guide path, before
extending it into a sequence of configurations in static equilibrium.

@@

\subsection{Computation of a guide path --- \Pa}
We first consider the problem of planning a root guide path (Figure~\ref{fig:framework}--$\mathcal{P}_1$).  The dimension of the path is equal to the number of degrees of freedom of the root of the robot.
Similarly to previous work~\citep{Bouyarmane2009} the path must be \textit{equilibrium feasible}: the root configurations must be extensible into full-body static equilibrium configurations. Previous work verifies \textit{equilibrium feasibility} by explicitly computing such a configuration. 
We preserve the low dimensionality of the problem by approximating \textit{equilibrium feasibility} with \textit{contact rechability}, illustrated in the following.

An intuitive description of \gls{contact reachable} configurations is ``close, but not too close'' to the environment: close, because a contact surface must be partially included in the reachable workspace of the robot (represented for the right leg in Figure~\ref{fig:contact_gen}--a) to allow contact creation; not too close, because the robot must avoid collision.
%~ \deladp{\textit{Contact reachability} is verified with the \textit{reachability condition}, a geometrical criterion based on this intuitive description (Figure~\ref{fig:reach_cond}).}
More precisely, a root configuration is \textit{contact reachable} if the root scaled by a user-defined factor $s \geq 1$ is not in collision, while the reachable workspace is in collision.
%~ Verifying the \textit{reachability condition} is very efficient in practice.
To plan a root path, we then use an RRT planner where, instead of checking collision to validate a configuration, we verify the \textit{reachability condition}.
This is detailed in Section~\ref{rbprm}.
%~ In Section~\ref{rbprm} we detail how  we define and use the \textit{reachability condition} to compute a guide path with the Reachability-Based RRT (Figure~\ref{fig:framework}---\Pa).

@@

The algorithm takes advantage of the fact that each root configuration is fixed to generate the contact by considering each limb individually. Candidate limb configurations resulting in the end-effector being close to the environment are selected from a database computed offline independently from the environment).
Then we select one of these configurations based on user-defined heuristics (Figure~\ref{fig:contact_gen}), detailed in Appendix~\ref{sec:heuristics}.

@@

\section{Notation and definitions} \label{notations}
